From Big Data to Big Displays\\ High-Performance Visualization at Blue Brain

### 2017-05-10 paper.tex
http server, python API

The http server is built using cppnetlib \cite{cppnetlib} for the transport and
http protocol handling. It supports all standard http verbs (GET, POST, PUT,
PATCH, DELETE). It is a \textsf{zeroeq::Receiver}, that is, it can share its
\textsf{receive()} update operation with other subscribers and http servers.
Unlike a subscriber, the http server follows the HTTP request-reply semantics,
that is, a request received by a server has to be followed directly by its
reply. future

vocabulary

\section{Rendering Applications}
\subsection{Interactive Raytracing}

>>>>

The http server is built using cppnetlib~\cite{cppnetlib} for the transport and
http protocol handling. It supports all standard http verbs (GET, POST, PUT,
PATCH, DELETE). It is a \textsf{zeroeq::Receiver}, that is, it can share its
\textsf{receive()} update operation with other subscribers and http servers.
Unlike a subscriber, the http server follows the HTTP request-reply semantics,
that is, a request received by a server has to be followed directly by its
reply. To allow asynchronous request processing, the return value from the
request handler is a \textsf{std::future} which is retrieved from an internal
thread, thus allowing the application to continue operations.

The http server is introspectable, it allows querying the available endpoints
(objects) and the JSON schema~\cite{jsonschema} for each endpoint.
\lref{lhttpReg} shows an excerpt of the Tide registry, and \lref{lhttpSchema} an
excerpt of the schema for one of the exposed objects. This REST API is used by
the Tide web interface from Javascript and to generate remote python APIs.

\noindent\begin{minipage}[b][][b]{.48\textwidth}
\begin{lstlisting}[caption=HTTP Server Registry, label=lhttpReg]
> GET /registry HTTP/1.0
{
[...]
   "tide/open" : [ "PUT" ],
   "tide/options" : [ "GET", "PUT" ],
   "tide/resize-window" : [ "PUT" ],
[...]
}
\end{lstlisting}
\end{minipage}\hfill
\begin{minipage}[b][][b]{.48\textwidth}
\begin{lstlisting}[caption=Object JSON Schema, label=lhttpSchema]
> GET /tide/options/schema HTTP/1.0
{
[...]
    "properties": {
        "alphaBlending": {
            "type": "boolean"
        },
[...]
}
\end{lstlisting}
\end{minipage}

\subsection{Remote Python API}

The remote python API provides easy to use access to remote applications using
the http server. It integrates two features: generic code generation for the
REST API exposed by the application, and automatic resource allocation and
application launch.

The generic code generation is implemented in a pure python module, which has
no dependency to the interfaced C++ application. It queries the http server and
generates a python API for all exposed objects. This API can then be
conveniently used in python to remote control the application.

Access to the application is established either through an explicit connection
of a pre-launched application, or via a resource allocator. The allocator hides
the details of allocating a resource, e.g. using a scheduling system like
slurm, launching and connecting to the launched application from the python
programmer.

\section{Rendering Applications}

The rendering applications form the backbone of our ecosystem.

\subsection{Interactive Raytracing}

\subsection{OpenGL Parallel Rendering}
